Increased Education Level of Women Associates with Higher Occupational Prestige and Happiness

### 2023-03-16 outputs/paper/paper.qmd
grammar edits

In this paper, the analysis will be carried out using the statistical programming language `R` [@citeR], using the `haven` [@citeHaven] and `tidyverse` [@citeTidy] packages. All figures in the report are generated using `ggplot2` [@citeGG].

@@

In this case, the survey focuses on US citizens who are adults and living in households. The data frame includes adults that are 18 and over that are living in households. The sample is voluntary and randomly selected from households. The survey relies on probability sampling, specifically simple random sampling, which ensures the validity of the survey. However, this type of sampling can be expensive, and some households may opt-out, which reduces the expected sample size. Non-response does not result in any penalty. The main goal of the survey is to gather information about American society to discern trends in attitudes and behaviors. One of the strengths of this survey is that it is highly respected and serves as a gold standard in social science research, with a 50-year history of successful data collection. However, one of the weaknesses is that one person represents 90,000 people, and if one person chooses not to participate, a large number of voices are lost.

This report provides an analysis of the questionnaire used in the General Social Survey (GSS). The GSS questionnaire covers a wide range of topics, which offers social science researchers a great deal of flexibility in their analyses. In this survey, a vast variety of topics means there are tons of angles that social science researchers could take with the GSS. Additionally, the bi-annual aspect of the survey means that the survey can be catered to trends and world events that have occurred, or are occurring.

Another strength is that public trust of the survey is backed by its history, which means that very little worry about privacy concerns due to a good history of keeping privacy protected. Furthermore, the bi-annual nature of the survey enables it to be updated in response to current trends and world events. The GSS has a long history of privacy protection, which enhances public trust in the survey.

On the negative side, the questionnaire is too general, requiring supplementary research to provide a specific focus on certain aspects of the GSS. While this is not necessarily a bad thing, it can limit the quality of data collected. Moreover, the breadth of the survey lets researchers ask the questions they want to ask before they delve deep to find answers. As stated before, there are too little respondents, there should be more for better quality of data. Additionally, there are relatively few respondents, which can undermine the validity of the data.

>>>>

In this paper, the analysis will be carried out using the statistical programming language `R` [@citeR], using the `haven` [@citeHaven] and `tidyverse` [@citeTidy] packages. All figures in the report are generated using `ggplot2`[@citeGG].

@@

In this case, the survey focuses on American adults. The data frame includes adults 18 and over living in households. The sample is voluntary and randomly selected. The survey relies on probability sampling, specifically simple random sampling, which ensures the validity of the survey. However, this type of sampling can be expensive, which may cause some households to opt-out and reduce the expected sample size. Non-response does not result in any penalty. The main goal of the survey is to gather information about American society in order to discern trends in attitudes and behaviors. One of the strengths of this survey is that it is highly respected and serves as a gold standard in social science research, with a 50-year history of successful data collection. However, one of the weaknesses is that one respondent is projected to represent 90,000 people [@citeGSS]. Therefore, if one person chooses not to participate, a large number of voices are lost and unheard.

This report provides an analysis of the questionnaire used in the General Social Survey (GSS). The GSS questionnaire covers a wide range of topics, which offers social science researchers immense flexibility in their analyses, enabling their research to be from numerous angles. Additionally, the frequency of the survey being collected every other year means that the survey can be catered to trends and world events that have occurred, or are occurring. Another strength is the high public trust of the survey because of its long history. Due to the survey's history of keeping privacy protected, there are very few privacy concerns or complaints.

On the negative side, the questionnaire is very general, requiring supplementary research to provide a specific focus on certain aspects of the GSS. While this is not necessarily a negative aspect, it can limit the quality of data collected. Moreover, the breadth of the survey enables researchers to examine the key questions they want to ask before they delve deep to find answers. Finally, as stated before, there are too few respondents, which may undermine the quality and validity of the data.
